---
title: "Image Denoise Project Workflow"
author: "R10898 Team"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    highlight: tango
    code_folding: show
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(DT)
library(ggplot2)
```

# Project Overview

This document outlines the complete workflow for the **Image Denoise Project**, which processes raw image data collected by the technical team for noise reduction analysis and training dataset preparation.

## Workflow Summary

The project consists of several automated processing steps followed by manual quality control and final data organization for training purposes.

---

# Data Access & Setup

## Initial Data Collection

Raw image data is collected by the technical team at the **119 server** and accessed from the **114 server**.

**TODO:** 🔍 *How to distinguish used and unused data? 114 Writing permission?*

```{bash data-access}
# Access raw data from 119 server to 114 server
# Raw data location: /mnt/data/R10898/ai_jz2_test
ls -la /mnt/data/R10898/ai_jz2_test
```

---

# Step 1: Format Conversion (Raw → PNG)

## Script Information
- **Script**: `/mnt/sfs_turbo/R10898/n2n_dataprocess/yuv420nv12_processor.py`
- **Duration**: ~15 minutes
- **Purpose**: Convert raw image format to PNG folders

## Input/Output

| Parameter | Path |
|-----------|------|
| **Input** | `/mnt/data/R10898/ai_jz2_test` |
| **Output** | `/mnt/data/R10898/ai_jz2_test_PNG` |
| **Summary** | `/mnt/data/R10898/ai_jz2_test_PNG/yuv_png_20250717_022208.txt` |

## Execution

```{bash step1-conversion}
# Execute YUV to PNG conversion
python /mnt/sfs_turbo/R10898/n2n_dataprocess/yuv420nv12_processor.py \
  --input /mnt/data/R10898/ai_jz2_test \
  --output /mnt/data/R10898/ai_jz2_test_PNG

# Check conversion summary
cat /mnt/data/R10898/ai_jz2_test_PNG/yuv_png_20250717_022208.txt
```

## Validation

```{bash step1-validation}
# Verify output structure
echo "=== PNG Conversion Results ==="
find /mnt/data/R10898/ai_jz2_test_PNG -type d -maxdepth 2 | head -10
echo "Total PNG folders created:"
find /mnt/data/R10898/ai_jz2_test_PNG -type d -name "*PNG*" | wc -l
```

---

# Step 2: Random Sampling by ISO

## Script Information
- **Script**: `/mnt/sfs_turbo/R10898/n2n_dataprocess/random_sample_by_iso.py`
- **Duration**: ~1 minute
- **Purpose**: Pull 50 PNG folders from each gain level

## Input/Output

| Parameter | Path |
|-----------|------|
| **Input** | `/mnt/data/R10898/ai_jz2_test_PNG` |
| **Output** | `/mnt/data/R10898/ai_jz2_test_PNG_50` |
| **Summary** | `/mnt/data/R10898/ai_jz2_test_PNG_50/random_sampling_report_20250717_024530.txt` |

## Execution

```{bash step2-sampling}
# Execute random sampling by ISO
python /mnt/sfs_turbo/R10898/n2n_dataprocess/random_sample_by_iso.py \
  --input /mnt/data/R10898/ai_jz2_test_PNG \
  --output /mnt/data/R10898/ai_jz2_test_PNG_50 \
  --samples_per_iso 50

# Review sampling report
cat /mnt/data/R10898/ai_jz2_test_PNG_50/random_sampling_report_20250717_024530.txt
```

## Sampling Analysis

```{r step2-analysis}
# Read sampling report for analysis
sampling_report <- "/mnt/data/R10898/ai_jz2_test_PNG_50/random_sampling_report_20250717_024530.txt"

# Analyze ISO distribution in sampled data
# This would be replaced with actual data reading logic
cat("Sampling completed successfully\n")
cat("Check the report file for detailed ISO distribution\n")
```

---

# Step 3: PNG Set Structuring

## Script Information
- **Script**: `/mnt/sfs_turbo/R10898/n2n_dataprocess/process_png_sets_standalone.py`
- **Duration**: ~15 minutes
- **Purpose**: Structure PNGs to sets and associate different images for camera movement detection

## Input/Output

| Parameter | Path |
|-----------|------|
| **Input** | `/mnt/data/R10898/ai_jz2_test_PNG_50` |
| **Output** | `/mnt/data/R10898/ai_jz2_test_PNG_50_sets` |
| **Summary** | `/mnt/data/R10898/ai_jz2_test_PNG_50_sets/png_sets_processing_report_20250717_031501.txt` |

## Execution

```{bash step3-structuring}
# Execute PNG set structuring
python /mnt/sfs_turbo/R10898/n2n_dataprocess/process_png_sets_standalone.py \
  --input /mnt/data/R10898/ai_jz2_test_PNG_50 \
  --output /mnt/data/R10898/ai_jz2_test_PNG_50_sets

# Review processing report
echo "=== PNG Sets Processing Report ==="
cat /mnt/data/R10898/ai_jz2_test_PNG_50_sets/png_sets_processing_report_20250717_031501.txt
```

## Set Structure Validation

```{bash step3-validation}
# Analyze set structure
echo "=== Set Structure Analysis ==="
echo "Total sets created:"
find /mnt/data/R10898/ai_jz2_test_PNG_50_sets -maxdepth 1 -type d | wc -l

echo "Sample set structure:"
find /mnt/data/R10898/ai_jz2_test_PNG_50_sets -maxdepth 2 -type d | head -10
```

---

# Manual Quality Control Phase

## Data Segmentation for Manual Review

After automated processing, the data requires manual quality assessment by interns.

### Manual Process Workflow:

1. **Distribution**: PNG sets are distributed to interns for manual review
2. **Classification**: Interns manually categorize sets into:
   - ✅ **Qualified folder**: High-quality image sets
   - ❌ **Unqualified folder**: Poor-quality image sets
3. **Collection**: Processed data collected from individual intern laptops

```{bash manual-setup}
# Prepare directories for manual review distribution
# This would typically be done on individual intern machines

echo "=== Manual Review Setup ==="
echo "1. Create qualified/unqualified directories on intern laptops"
echo "2. Distribute PNG sets for manual review"
echo "3. Interns classify sets based on quality criteria"

# Example directory structure for interns:
# ~/manual_review/
# ├── qualified/
# ├── unqualified/
# └── original_sets/
```

## Data Collection from Interns

```{bash manual-collection}
# Collect manually processed data from interns
# Merge back on 114 server to restore original directory structure

echo "=== Data Collection Process ==="
echo "1. Collect qualified/unqualified classifications from each intern"
echo "2. Merge data back to 114 server"
echo "3. Restore original directory structure with quality labels"
```

---

# Final Processing & ISO Reorganization

## Script Information
- **Script**: `/mnt/sfs_turbo/R10898/n2n_dataprocess/reorganize_by_iso.py`
- **Purpose**: Restructure datasets based on ISO values for training and generate distribution plot

**TODO:** 🔍 *Might need to adjust the "qualified" and PNGs folders level?*

## Input/Output

| Parameter | Path |
|-----------|------|
| **Input** | `/mnt/data/R10898/ai_jz2_test_PNG_50_sets` |
| **Output Dataset** | `/mnt/data/R10898/ai_jz2_test_PNG_50_sets_ISO` |
| **Output Plot** | `/mnt/data/R10898/ai_jz2_test_PNG_50_sets_ISO/iso_distribution_plot_20250717_033018.png` |

## Execution

```{bash final-processing}
# Execute ISO-based reorganization
python /mnt/sfs_turbo/R10898/n2n_dataprocess/reorganize_by_iso.py \
  --input /mnt/data/R10898/ai_jz2_test_PNG_50_sets \
  --output /mnt/data/R10898/ai_jz2_test_PNG_50_sets_ISO \
  --generate_plot true

echo "=== Final Dataset Structure ==="
ls -la /mnt/data/R10898/ai_jz2_test_PNG_50_sets_ISO/
```

## ISO Distribution Analysis

```{r iso-analysis}
# Analyze ISO distribution in final dataset
# Note: This would require actual data reading in a real implementation

cat("=== ISO Distribution Analysis ===\n")
cat("Plot generated: iso_distribution_plot_20250717_033018.png\n")
cat("Dataset organized by ISO values for training\n")

# If the plot file exists, we could include it
plot_path <- "/mnt/data/R10898/ai_jz2_test_PNG_50_sets_ISO/iso_distribution_plot_20250717_033018.png"
cat(paste("Plot file location:", plot_path, "\n"))
```

---

# Project Deliverables

## Final Distribution

### 1. Training Dataset
- **Recipient**: 周哥
- **Content**: Restructured dataset organized by ISO values
- **Location**: `/mnt/data/R10898/ai_jz2_test_PNG_50_sets_ISO`

### 2. Analysis Report
- **Recipient**: Data Collection Team
- **Content**: ISO distribution plot and processing summary
- **Location**: `iso_distribution_plot_20250717_033018.png`

```{bash deliverables}
echo "=== Project Deliverables Summary ==="
echo "1. Training Dataset for 周哥:"
du -sh /mnt/data/R10898/ai_jz2_test_PNG_50_sets_ISO

echo "2. ISO Distribution Plot for Collection Team:"
ls -la /mnt/data/R10898/ai_jz2_test_PNG_50_sets_ISO/*.png
```

---

# Quality Metrics & Summary

## Processing Statistics

```{r quality-metrics}
# Summary of processing pipeline
cat("=== Processing Pipeline Summary ===\n")

stages <- data.frame(
  Stage = c("Raw Data", "PNG Conversion", "Random Sampling", "Set Structuring", "Manual Review", "ISO Organization"),
  Duration = c("N/A", "~15 min", "~1 min", "~15 min", "Manual", "Variable"),
  Input_Location = c("/mnt/data/R10898/ai_jz2_test", 
                    "/mnt/data/R10898/ai_jz2_test",
                    "/mnt/data/R10898/ai_jz2_test_PNG",
                    "/mnt/data/R10898/ai_jz2_test_PNG_50",
                    "/mnt/data/R10898/ai_jz2_test_PNG_50_sets",
                    "/mnt/data/R10898/ai_jz2_test_PNG_50_sets"),
  Output_Location = c("N/A",
                     "/mnt/data/R10898/ai_jz2_test_PNG",
                     "/mnt/data/R10898/ai_jz2_test_PNG_50", 
                     "/mnt/data/R10898/ai_jz2_test_PNG_50_sets",
                     "Intern laptops",
                     "/mnt/data/R10898/ai_jz2_test_PNG_50_sets_ISO")
)

kable(stages, caption = "Image Denoise Project Processing Pipeline")
```

## Outstanding TODOs

```{r todos}
todos <- data.frame(
  Priority = c("High", "Medium"),
  Task = c("Resolve data usage tracking and 114 server writing permissions",
           "Evaluate and potentially adjust qualified/PNGs folder hierarchy"),
  Location = c("Data Access Phase", "Final Processing Phase"),
  Status = c("Open", "Open")
)

kable(todos, caption = "Outstanding Project TODOs")
```

---

# Appendix

## File Structure Overview

```
/mnt/data/R10898/
├── ai_jz2_test/                    # Raw input data
├── ai_jz2_test_PNG/               # Step 1 output
├── ai_jz2_test_PNG_50/            # Step 2 output  
├── ai_jz2_test_PNG_50_sets/       # Step 3 output
└── ai_jz2_test_PNG_50_sets_ISO/   # Final output
```

## Script Locations

```
/mnt/sfs_turbo/R10898/n2n_dataprocess/
├── yuv420nv12_processor.py        # Format conversion
├── random_sample_by_iso.py        # ISO sampling
├── process_png_sets_standalone.py # Set structuring
└── reorganize_by_iso.py           # Final organization
```

---

*Document generated on `r Sys.Date()` for the Image Denoise Project workflow documentation.* 